### 2014-11-07 intro.tex
edits

To address these issues, we describe \name, a declarative programming model
and implementation for eventually consistent geo-distributed data
stores. The key novelty of \name is an expressive \emph{contract language}
to declare and verify fine-grained application-level consistency
properties. The programmer uses the contract language to axiomatically
specify the set of legal executions allowed over the replicated data
type. Contracts are constructed using primitive consistency relations such
as \emph{visibility} and \emph{session order} along with standard logical
and relational operators. A \emph{contract enforcement system} automatically
maps operations over the datatype to a particular consistency level
available on the store, and provably validates the correctness of the
mapping.  The paper makes the following contributions:

\begin{itemize}
\setlength{\itemsep}{2pt}
\item We introduce \name, a shallow extension of Haskell that supports the
	description and validation of replicated data types found on eventually
	consistent stores. Contracts are used to specify fine-grained
	application-level consistency properties, and are analyzed to assign the most
	efficient and sound store consistency level to the corresponding operation.
\item \name supports coordination-free transactions over arbitrary datatypes.
	We extend our contract language to express fine-grained transaction isolation
	guarantees, and utilize the contract enforcement system to automatically
	assign the correct isolation level for a transaction.
\item We provide metatheory that certifies the soundness of our contract
	enforcement system, and ensures that an operation is only executed if the
	required conditions on consistency are met.
\item An implementation of \name as a transparent shim layer over
	Cassandra~\cite{Cassandra}, a well-known general-purpose data store.
	Experimental evaluation over a set of real-world applications, including a
	Twitter-like micro-blogging site and an eBay-like auction site illustrates
	the practicality of our approach.
\end{itemize}

>>>>

To address these issues, we describe \name, a declarative programming model and
implementation for eventually consistent geo-distributed data stores. The key
novelty of \name is an expressive \emph{contract language} to declare and
verify fine-grained application-level consistency properties. The programmer
uses the contract language to axiomatically specify the set of legal executions
allowed over the replicated data type. Contracts are constructed using
primitive consistency relations such as \emph{visibility} and \emph{session
order} along with standard logical and relational operators. A \emph{contract
enforcement system} statically maps operations over the datatype to a
particular consistency level available on the store, and provably validates the
correctness of the mapping. The paper makes the following contributions:

\begin{itemize}
\setlength{\itemsep}{2pt}
\item We introduce \name, a shallow extension of Haskell that supports the
	description and validation of replicated data types found on eventually
	consistent stores. Contracts are used to specify fine-grained
	application-level consistency properties, and are statically analyzed to
	assign the most efficient and sound store consistency level to the
	corresponding operation.
\item \name supports coordination-free transactions over arbitrary datatypes.
	We extend our contract language to express fine-grained transaction isolation
	guarantees, and utilize the contract enforcement system to automatically
	assign the correct isolation level for a transaction.
\item We provide metatheory that certifies the soundness of our contract
	enforcement system, and ensures that an operation is only executed if the
	required conditions on consistency are met.
\item An implementation of \name as a transparent shim layer over
	Cassandra~\cite{Cassandra}, a well-known general-purpose data store.
	Experimental evaluation over a set of real-world applications, including a
	Twitter-like micro-blogging site and an eBay-like auction site illustrates
	the practicality of our approach.
\end{itemize}
